Viscous Transport in Eroding Porous Media

### 2019-06-19 docs/transport/erosion_transport.tex
do the result section in transport paper

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four time steps.

@@

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. To understand the meaning of jump 
of $\tau$, we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
We also can get the idea why the maximum value of $\tau$ is smaller 
than the one in the case of 20 bodies . 
The most of the bodies in this case are smaller than those in the case of 20 bodies.
So when two neighboring trajectories are splitted on the left side by a smaller body they do not
travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
}

>>>>

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid in colormap during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four equispaced times.
Since the vorticity is equivalent to the shear stress and the erosion is faster in the regions where
the magnitude of the vorticity is larger,

@@

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. To understand the meaning of jump 
of $\tau$, we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
then rejoin with each other and the splitting-rejoining behavior causes the difference of $\tau$ with respect to the neighboring trajectories.   
We also can get the idea why the maximum value of $\tau$ is smaller 
than the one in the case of 20 bodies . 
The most of the bodies in this case are smaller than those in the case of 20 bodies.
So when two neighboring trajectories are splitted on the left side by a smaller body they do not
travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
}
